\vspace{-1in} \usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{CSEC-472 Authentication Paper} \\ [14pt] \huge A Security Analysis of the Lenel BlueDiamond \\

### 2020-03-08 paper/wireframe/wireframe.tex

BLE is a major part of this research. BLE is a Bluetooth protocol variant designed for low energy operations and such has a limited set of computing resources available. BLE does not need manual pairing to a device, meaning an application with the correct authentication data can pair automatically. Automated tools will gather preliminary data about the device by examining the GATT and Generic Access Profile (GAP) . The tool will copy he GATT over to an intermediary device and MITM all communications between the device and the application. With the device communication being intercepted, an Injection Free Attack can force a re-pairing and the intermediary device will intercept the Short Term Key. With the Short Term Key, we can derive the Long Term Key. We can then use the Long Term Key to decrypt communications and send commands on the behalf of the application. Automated tools will scan the application to discover hard-coded credentials and vulnerabilities. Finally, edge cases in the authentication scheme will be manually explored to see if an attacker could exploit permissions.

>>>>

BLE is a major part of this research. BLE is a Bluetooth protocol variant designed for low energy operations and such has a limited set of computing resources available. BLE does not need manual pairing to a device, meaning an application with the correct authentication data can pair automatically. Automated tools will gather preliminary data about the device by examining the GATT and Generic Access Profile (GAP) . The tool will copy he GATT over to an intermediary device and MITM all communications between the device and the application. With the device communication being intercepted, an Injection Free Attack can force a re-pairing and the intermediary device will intercept the Short Term Key. With the Short Term Key,  An attacker can derive the Long Term Key. They can then use the Long Term Key to decrypt communications and send commands on the behalf of the application. Automated tools will scan the application to discover hard-coded credentials and vulnerabilities. Finally, edge cases in the authentication scheme will be manually explored to see if an attacker could exploit permissions.
